You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-24 paper/paper.tex
a bit of progress on writing...

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
paraphrase systems targeting a specific style of writing.
%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
%insufficient when the goal is to generate paraphrases targeting a specific style, and
%propose a series of new metrics to measure how closely the generated paraphrases match the target
%style.  
We empirically show that even with a relatively small amount of parallel training data available, it is
possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
baselines based on dictionaries and out-of-domain parallel text.
In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
To the best of our knowledge this is the first work to investigate the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

@@

Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.  
Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information information about a new product
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

In this paper, we investigate the task of automatic paraphrasing when targeting a specific writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help literature students to better understand Shakespeare.  These modern translations are used to generate a parallel corpus of Shakespere's style and modern English,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in shakesperean english, or parallel monolingual text
gathered through Amazon's Mechanical Turk \cite{chen11}.

We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of these automatic metrics
to capture the notion of writing style.  We propose several new metrics for evaluating the task of paraphrasing while targeting a specific style, and measure correlation with human judgement showing
promising results for this particular style.

Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
style of authors they are studying.  Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
paraphrasing in the other direction, this work also has the potential to make the other 20 plays more accessable to students of Shakespeare.

@@

\section{Data}
We propose to use Shakespeare's plays and their modern English translations as a testbed the task of paraphrasing targeting a specific writing style.  Having access to parallel text in the target
style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us
two reference translations for 8 out of the 17 plays.

After tokenizing and lowercasing, the plays and their modern translations were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner producing about 21,079 alignments out of 31,718 sentences
in the Sparknotes data, and 10,365 aligned sentence pairs out of 13,640 sentences in the enotes data.  In addition, we note that the modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ more significantly from the original texts, whereas the enotes data tends to stick closer to the original text, being much more conservative
in it's use of paraphrase, although it does include many useful paraphrses which do tend to be qualitatively different from those used in the Sparknotes data. %TODO: need examples of differences between the corpora?
To illustrate these differences empircally, we evaluated a very simple paraphrase system using the standard BLEU evaluation metric which has been shown to be a useful measure of semantic equivelance
in Parapharse \cite{chen11}.
These corpus statistics are summarized in table \ref{corpus_stats}.

@@

\begin{itemize}
  \item Motivate the need for a benchmark dataset for evaluating the writing style paraphrase task
  \item Present Shakespeare / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
\end{itemize}

>>>>

\begin{document}
\maketitle
%% The first mandatory ABSTRACT (\abstractEn) section below is for the English language
\abstractEn{  %ABSTRACT}{
We present initial investigation into the task of paraphrasing language while targeting a particular writing style.
The plays of William Shakespeare and their modern translations are used as a testbed for evaluating
paraphrase systems targeting a specific style of writing.
%We demonstrate that existing evaluation metrics developed in the Machine Translation and Paraphrase communities are
%insufficient when the goal is to generate paraphrases targeting a specific style, and
%propose a series of new metrics to measure how closely the generated paraphrases match the target
%style.  
We show that even with a relatively small amount of parallel training data available, it is
possible to learn paraphrase models which capture stylistic phenomenon, and these models outperform
baselines based on dictionaries and out-of-domain parallel text.
In addition we present an initial investigation into automatic evaluation metrics for paraphrasing writing style.
To the best of our knowledge this is the first work to investigate the task of
paraphrasing text with the goal of targeting a specific style of writing.
}

@@

Identical meaning can be expressed or \emph{paraphrased} in many different ways; automatically detecting or generating different expressions with the same meaning is 
fundamental to many natural language understanding tasks\cite{Giampiccolo07}, so much previous work has investigated methods for automatic paraphrasing\cite{Barzilay03,dolan04,Shinyama03,Das09,bannard05}.  
Although two utternaces may be semantically equivelant, they can still be stylistically quite different.  For example, the same information
is likely to be conveyed using very different lexical and grammatical patterns in advertising materials v.s. technical manuals, or in Shakespearean plays v.s. Hollywood movies.

In this paper, we investigate the task of automatic paraphrasing when targeting a writing style, focusing specifically on the style of Early Modern English employed by William Shakespeare.
We exploit modern translations of 17 plays written to help students better understand Shakespeare's work.  A parallel corpus is extracted from these modern translations,
which is then used to train phrase-based translation models which are capable of automatically paraphrasing ordinary sentences into Shakesperean English.  In addition we develop several
baseline systems which don't make use of this source of parallel text and instead rely on dictionaries of expressions commonly found in Shakesperean english, or parallel monolingual text
gathered through Amazon's Mechanical Turk \cite{chen11}.

We evaluate these models both through human judgements and standard evaluation metrics from the Machine Translation and paraphrase literature, however no previous work has investigated the ability of these automatic metrics
to capture the notion of writing style.  We propose several new metrics for evaluating paraphrases targeting a specific writing style, and measure correlation with human judgements showing  promising, yet
preliminary results.

Systems which are capable of automatically paraphrasing literary writing styles could be directly benefical for educational applications, for example helping students to experiment with writing literature in the
style of authors they are studying.  Additionally note that out of the 37 surviving plays written by William Shakespeare, only 17 currently have modern translations available; although we have not yet formally evaluated
paraphrasing in the other direction, we believe this work also has the potential to make the other 20 plays more accessable to students of Shakespeare by automatically generating relatively high-quality modern translations.

@@

\section{Data}
We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.

\subsection{Modern Translations}
We propose to use Shakespeare's plays and their modern English translations as a testbed for the task of paraphrasing while targeting a specific writing style.  Having access to parallel text in the target
style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us
two reference translations for 8 out of the 17 plays.

After tokenizing and lowercasing, the plays were aligned using Bob Moore's bilingual sentence \cite{Moore02} aligner, which produced about 21,079 alignments out of 31,718 sentences
in the Sparknotes data, and 10,365 sentence pairs out of 13,640 sentences in the enotes data.  The modern translations from each source are qualitatively quite
different.  The Sparknotes paraphrases tend to differ significantly from the original text, whereas the enotes translations are much more conservative, making fewer changes.
To illustrate these differences empirically and provide an initial paraphrase baseline, we computed BLEU scores of the unchanged modern translations against Shakespeare's 
original text; the Sparknotes paraphrases result in a BLEU score of 23.67, whereas the Enotes paraphrases prouce a much higher BLEU of 49.60 indicating their similarity to the original text.
These corpus statistics are summarized in table \ref{corpus_stats}.

\subsection{Dictionaries}

\subsection{Out of Domain Monolingual Parallel Data}

@@

\begin{comment}
\begin{itemize}
  \item Motivate the need for a benchmark dataset for evaluating the writing style paraphrase task
  \item Present Shakespeare / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
\end{itemize}
\end{comment}
